---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tabulka()

The goal of tabulka() is to make some nice tables.


## Installation

You can install tabulka from github with:

```R
# install.packages("devtools")
devtools::install_github("ljanda/tabulka")
```

## Examples

```{r, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
devtools::install_github("ljanda/tabulka")
library(tabulka)
data("diamonds")
```



### n_pct()
The n_pct() function gives a nicely formatted table for a 
categorical variable with the count and percent for each 
category. The table is arranged using the percent in 
descending order so that the biggest categories are 
at the top of the table. 

```{r, warning=FALSE, message=FALSE}
tabulka::n_pct(diamonds, cut)
```

### n_pct_fct()
The n_pct_fct() function gives a nicely formatted table for a 
factor variable with the count and percent for each 
factor. The table is arranged using the factor levels 
so that the preferred order is maintained.  

```{r, warning=FALSE, message=FALSE}
tabulka::n_pct_fct(diamonds, cut)
```


### shelve()
The shelve() function gives a nicely formatted table 
giving the Q1, Median, Mean, and Q3 for a 
continous variable that is broken down by categories from 
a categorical variable 

```{r, warning=FALSE, message=FALSE}
tabulka::shelve(diamonds, cut, price)
```
